Logarithmic Space Verifiers on NP-complete

### 2019-11-12 doc/manuscript.tex
Updated the content proof

\begin{theorem}
\label{closed}
If $T(n)$ is such that
\[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
then $\textit{1TAPE}[T(n)]$ is closed under deterministic two-way logarithmic space reduction.
\end{theorem}

@@

\begin{proof}
Hartmanis and Mahaney have shown that $1NL \varsubsetneq \textit{1TAPE}[T(n)]$ when
\[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
in their paper \cite{HM81}. Consequently, this is a consequence of Theorem \ref{closed}, because $1NL$ is also closed under deterministic two-way logarithmic space reduction.
\end{proof}

>>>>

\begin{theorem}
\label{closed}
If $T(n)$ is such that
\[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
and is not a constant, then $\textit{1TAPE}[T(n)]$ is closed under deterministic two-way logarithmic space reduction.
\end{theorem}

@@

\begin{proof}
Hartmanis and Mahaney have shown that $1NL \varsubsetneq \textit{1TAPE}[T(n)]$ when
\[\lim_{n\to\infty} \frac{T(n)}{n} = 0\]
in their paper \cite{HM81}. Consequently, this is a result of Theorem \ref{closed}, because $1NL$ is also closed under deterministic two-way logarithmic space reduction.
\end{proof}
